imputation_stickle

### 2025-09-29 R/StickleImputationCode.Rmd
updated imputation code.

>>>>

```{r}
combined_csv <- read.csv("../Data/updated_stickle_imputations_100_20250904.csv")
combined_csv %>% group_by(imp) %>% summarize(percent_male = 100*mean(gender == "Male")) %>% ggplot(aes(x = percent_male)) + geom_density() + theme_bw() + xlab("Percent Male")
```

# Cross validation

```{r}
set.seed(2025)
stick_extant <- stick %>% filter(substring(univID,1,3) != "Fos") 
stick_extant$ind <- sample(rep(1:5,75), nrow(stick_extant),replace = FALSE)

M <- 100
preds <- list()
for (i in 1:5){
temp <- stick_extant 
temp$gender[temp$ind == i] <- NA
imp_temp <- mice(temp %>% select(-ind),m = M)
comp_temp <- complete(imp_temp, "long")
comp_temp$ind <- rep(temp$ind,M)
comp_temp <- comp_temp %>% mutate(gender_true = rep(stick_extant$gender,M)) %>% filter(ind == i) 
preds[[i]] <- comp_temp %>% group_by(.id, gender_true) %>% summarize(pct_male = mean(gender == "Male"))
}

stack <- do.call(rbind,preds)

library(ROCR)
roc_pred <- prediction(stack$pct_male, stack$gender_true)
auc_rocr <- performance(roc_pred, measure="auc")
perf <- performance(roc_pred, measure="tpr", x.measure="fpr")
data.frame(FPR = perf@x.values[[1]], TPR = perf@y.values[[1]]) %>% ggplot(aes(x = FPR,y = TPR)) + geom_line() + theme_bw() + geom_abline(slope = 1, linetype = 3)
```

### 2025-09-29 R/stickle_imputation.Rmd
updated imputation code.

```{r}
stickle <- read_csv('stickle_revamped.csv')

@@

stick

>>>>

 <!-- LQx.B.M.139 was called male in hand (and in our database) but is female by dissection. -->
 <!-- LQx.B.M.155 was called male in hand (and in our database) but is female by dissection. -->
 <!--     Pax.B.M.081 was called male in hand (and in our database) but is female by dissection. -->
 <!--     Pax.L.M.113 was called male in hand (and in our database) but is female by dissection. -->
 <!--     Pax.L.M.115 was called male in hand (and in our database) but is female by dissection. -->

```{r}
stickle <- read_csv('../Data/Stickle_revamped.csv')

@@

#Manual Fixes
 # <!-- LQx.B.M.139 was called male in hand (and in our database) but is female by dissection. -->
 # <!-- LQx.B.M.155 was called male in hand (and in our database) but is female by dissection. -->
 # <!--     Pax.B.M.081 was called male in hand (and in our database) but is female by dissection. -->
 # <!--     Pax.L.M.113 was called male in hand (and in our database) but is female by dissection. -->
 # <!--     Pax.L.M.115 was called male in hand (and in our database) but is female by dissection. -->
stick$gender[stick$univID == "LQx.B.M.139"] <- "Female"
#stick$gender[stick$univID == "LQx.B.M.155"] <- "Female"
stick$gender[stick$univID == "Pax.B.M.081"] <- "Female"
stick$gender[stick$univID == "Pax.L.M.113"]<- "Female"
stick$gender[stick$univID == "Pax.L.M.115"] <- "Female"

#Exploring the ones that were changed
stick %>% filter(univID %in% c("LQx.B.M.139","Pax.B.M.081","Pax.L.M.113","Pax.L.M.115"))

stick %>% mutate(changed = univID %in% c("LQx.B.M.139","Pax.B.M.081","Pax.L.M.113","Pax.L.M.115")) %>% filter(changed) %>% ggplot(aes(x = ds3, y = lps, col = changed)) + geom_point(alpha = 0.5)

stick %>% mutate(changed = univID %in% c("LQx.B.M.139","Pax.B.M.081","Pax.L.M.113","Pax.L.M.115"))  %>% ggplot(aes(x = changed, y = lps, color = changed)) + geom_boxplot() + geom_jitter()

stick %>% mutate(changed = univID %in% c("LQx.B.M.139","Pax.B.M.081","Pax.L.M.113","Pax.L.M.115"))  %>% ggplot(aes(x = changed, y = ds3, color = changed)) + geom_boxplot() + geom_jitter()
